Introduction to *cellcount* - Draft vignette

### 2022-12-15 cellcount_intro.Rmd
Updates
Updated

---
title: "Introduction to *cellcount*"
author: "*T.E. Harman, M. Vandersea, D.E. Berthold, H.D. Laughinghouse, B. Boyd, K. Pokrzywinski*"
date: "__/__/2022"
abstract: >
  The *cellcount* package provides wrapper functions for  [*EBImage*](http://bioconductor.org/packages/devel/bioc/vignettes/EBImage/inst/doc/EBImage-introduction.html) to simplfy quantifying bacteria and cyanobacteria via flourescence microscopy. Cyanobacteria enumeration is an important tool to incorporate data results into mathematical models to assess bloom dynamics. However, standard manual cyanobacteria enumeration is considered time-consuming and can impact overall random error due to different inaccuracies from researcher to researcher. Here, we outline a new open-source tool, *cellcount*, a package designed for the computing language R to assist with cyanobacteria enumeration. Fluorescent microscopy images are analyzed by this package to generate cyanobacteria counts to assess overall cell density from samples.
output: html_document
---

@@

@@

@@

>>>>

---
title: "Introduction to *cellcount* - Draft vignette"
author: "*T.E. Harman, M. Vandersea, D.E. Berthold, H.D. Laughinghouse, B. Boyd, K. Pokrzywinski*"
date: "12/15/2022"
abstract: >
  The *cellcount* package provides wrapper functions for  [*EBImage*](http://bioconductor.org/packages/devel/bioc/vignettes/EBImage/inst/doc/EBImage-introduction.html) to simplfy quantifying bacteria and cyanobacteria via flourescence microscopy. Cyanobacteria enumeration is an important tool to incorporate data results into mathematical models to assess bloom dynamics. However, standard manual cyanobacteria enumeration is considered time-consuming and can impact overall random error due to different inaccuracies from researcher to researcher. Here, we outline a new open-source tool, *cellcount*, a package designed for the computing language R to assist with cyanobacteria enumeration. Fluorescent microscopy images are analyzed by this package to generate cyanobacteria counts to assess overall cell density from samples.
output: html_document
---

@@

write.csv(Cell.Count, paste0(savdir, "/Anabena_test counts.csv"))

@@

write.csv(Cell.Count, paste0(savdir, "/Shewanella_test counts.csv"))

@@

Wetzel, RG and Likens, GE. 1991. Limnological Analyses, Second Edition. Springer-
Verlag. 391 pp.

Gregoire, P, Fuchs, F, Sklyar, O, Boutros, M, and Huber, W.
2010. EBImage - an R package for image processing with applications to cellular
phenotypes. Bioinformatics, 26(7), pp. 979-981, 10.1093/bioinformatics/btq046

Pokrzywinski, K, Boyd, B, Smith, J. 2019. A High-throughput Method for Counting 
Cyanobacteria Using Fluorescence Microscopy. ERDC TR-19-21.
